Co-methylation

### 2014-10-03 Rmarkdown/comethylation.Rmd
Tidying.

Long-read sequencing technologies, such as Pacific Biosciences (__CITE__) and Oxford Nanopore (__CITE__), would overcome this limitation but the lesser throughput of these technologies and the reliability with which they can identify methylcytosines create new complications (__CITE__). An alternative solution, although completely hypothetical, is to use a technique that generates synthetic long reads, similar to those generated by Illumina's TruSeq Synthetic Long-Read technique[^moleculo](__CITE__).

@@

__PREVIOUS WORK__

* \cite{Paliwal:2013fk}

>>>>

Long-read sequencing technologies, such as Pacific Biosciences (__CITE__), Roche 454 (__CITE__) and Oxford Nanopore (__CITE__), would overcome this limitation but the lesser throughput of these technologies and the reliability with which they can identify methylcytosines create new complications (__CITE__). An alternative solution, although completely hypothetical, is to use a technique that generates synthetic long reads, similar to those generated by Illumina's TruSeq Synthetic Long-Read technique[^moleculo](__CITE__).

@@
